---
title: "p8105_hw1_dl3757"
author: "Dang Lin dl3757"
date: "2024-09-21"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE}
# Import the "tidyverse" library
library(tidyverse)

# Import the "ggplot2" library
library(ggplot2)
```

## Problem 1
```{r, message = FALSE}
# Load the "penguins" data
data("penguins", package = "palmerpenguins")

# Remove the missing values in the dataset
penguins_clean <- penguins %>% na.omit()
```

The "penguins" dataset incorporates eight variables. Firstly, the dataset contains three species of penguins: Adelie, Gentoo, and Chinstrap, which are found on three different islands: Torgersen, Dream, and Biscoe. Besides, four numeric variables: bill length, bill depth, flipper length, and body mass of each penguin have been included in the dataset. Furthermore, this dataset also contains an ordinal variable "year", and a nominal data "sex" of the penguin. The "penguins" dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns, and the mean of flipper length is `r mean(penguins_clean$flipper_length_mm)` mm.
