---
title: "p8105_hw1_dl3757"
author: "Dang Lin dl3757"
date: "2024-09-21"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE}
# Import the "tidyverse" library
library(tidyverse)

# Import the "ggplot2" library
library(ggplot2)
```

## Problem 1
```{r, message = FALSE}
# Load the "penguins" data
data("penguins", package = "palmerpenguins")

# Remove the missing values in the dataset
penguins_clean <- penguins %>% na.omit()
```

The "penguins" dataset incorporates eight variables. Firstly, the dataset contains three species of penguins: Adelie, Gentoo, and Chinstrap, which are found on three different islands: Torgersen, Dream, and Biscoe. Besides, four numeric variables: bill length, bill depth, flipper length, and body mass of each penguin have been included in the dataset. Furthermore, this dataset also contains an ordinal variable "year", and a nominal data "sex" of the penguin. The "penguins" dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns, and the mean of flipper length is `r mean(penguins_clean$flipper_length_mm)` mm.

```{r}
# Make a scatterplot of Flipper Length vs. Bill Length
ggplot(penguins_clean, aes(y = flipper_length_mm, 
                           x = bill_length_mm, 
                           color = species)) + 
  geom_point() + 
  labs(x = 'Bill Length (mm)',
       y = 'Flipper Length (mm)',
       title = 'Flipper Length vs. Bill Length') + 
  theme_minimal()

# Export the scatterplot in PNG form
ggsave("flipper_length_vs_bill_length.png")
```

## Problem 2
```{r}
# Set seed for reproducibility
set.seed(3757)

# Create a data frame
df <- tibble(
  numeric_vector = rnorm(n = 10), 
  logical_vector = numeric_vector > 0, 
  character_vector = c("A", "B", "C", "D", "E", 
                       "F", "G", "H", "I", "J"), 
  
  factor_vector = factor(rep(c("Level_1", "Level_2", "Level_3"), 
                      length.out = 10))
)
```